Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2018-06-07 documents/Referee Responses/refereeresponses.tex

% === Revtex Declaration ===
\documentclass[]{article}

\usepackage{document_config}
\newcounter{refereecounter}
\newcounter{commentcounter}[refereecounter]
\newcommand{\getcommentlabel}{Comment \textbf{\arabic{refereecounter}.\arabic{commentcounter}}}
\newcommand{\getresponselabel}{Response \textbf{\arabic{refereecounter}.\arabic{commentcounter}}}
\usepackage[margin=0.5in]{geometry}

\newcommand{\ccomment}[1]{
    \vspace{1em}
    \stepcounter{commentcounter}
    \getcommentlabel \\
    \textcolor{darkgray}{\rule{\linewidth}{0.5pt}}
    \color{gray}
    #1
    \color{black}
}
\newcommand{\response}[1]{
    \vspace{1em}
    \getresponselabel \\
    \textcolor{darkgray}{\rule{\linewidth}{0.5pt}}
    #1
}
\setlength{\parindent}{0pt}

\begin{document}
    \begin{center}
        \textbf{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure} \\
        \textbf{[Referee Responses]} \\
        Thomas C. Fraser and Elie Wolfe \\
        Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5 \\
        University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1\\
        June 7, 2018
    \end{center}

@@

    \stepcounter{refereecounter}
    \section{Responses to First Referee}

    \ccomment{This work considers the derivation of tests for discriminating classical correlations from non-classical correlations in a three-party scenario in which causal influences are pairwise shared between all three players. Hence it is a "triangle scenario". The authors apply the recently developed inflation technique to derive several new inequalities satisfied by all classical correlations in the triangle scenario. Next, they numerically study the ability of quantum theory to violate them. A quantum distribution that doesn't have a classical model has previously known -- Fritz's distribution. This distribution has a central role for how the authors approach the problem. In particular they manage to derive inequalities, robust to a small amount of noise, that detect Fritz's distribution, and some `similar' quantum distributions.}

    \ccomment{This is a long and quite technical paper. Having read it, I understand that it is directed at a specialist audience knowledgeable on causal inference and/or network Bell inequalities. The comments that follow are made with this specialized audience in mind.}

    \ccomment{As the original work, presented in sections VI to VIII, is heavy based on numeric and the computer-implemented inflation technique, I have not considered it reasonable to try to check the correctness of any derivations or numerical claims. I simply trust the authors on this matter.}

    \ccomment{I think the paper is well-written. I had no troubles understanding the messages the authors presumably wished to convey. However, the paper is quite long. Therefore, I think it would benefit from a short and clear summary of what the main contribution of this paper is, and what the outlook is. This appears currently in the conclusions. However, I think it is worth outlining this much earlier in the paper, so that a reader knows what to expect from the long read. Practically, I am proposing that the part of the introduction in which the structure of the paper is presented, is expanded or supplemented.}

    \response{
        Fantastic suggestion; we have updated and adjusted the introduction to make the contributions of this paper more clear to the reader in two ways. First, when summarizing the organization of the manuscript, we make it explicit that the first half is dedicated to a review of previous works, while the second half includes the contributions made by the research. Second, when delineating the precise contributions made by the second half of the paper, we provide an overview of the main purposes for deriving these inequalities and how we explored their utility. The language used now more closely mirrors that of the conclusions. Hopefully, readers familiar, at least, with the subject matter of Bell inequalities will be able to comprehend the nature of the advancements made by this work from the introduction alone.
    }

    \ccomment{In general I appreciate this type of thorough basic research on a poorly understood topic by, due to currently lack of deep understanding, non-rigorous methods. I think it provides useful hints and shows the potential usefulness of the inflation technique for future work in this direction. By now, I believe it is well-established that it is a difficult matter to study quantum correlations in the triangle scenario. Therefore consider this type of investigations relevant.}

    \ccomment{I consider this paper suitable for PRA, since many previous works on quantum networks have been published here and therefore the right audience will probably notice it. I recommend it for publication, given that my more detailed comments, appearing below, are taken into consideration before either being (partially) addressed or discarded with a good motivation.}

    \ccomment{Regarding section VI. What is previously known about the inequalities of [21] and and [19]? Has nobody studied or attempted to violate these before? If yes, what were the results? I would be a bit surprised if triangle inequalities were derived but attempted to be violated by some super-classical model. Basically, I think it would be good to put the numerics for these inequalities into a bit more of a context.}

    \response{
    An excellent comment, thank you. We have elected to add more historical context to Section VI. Specifically, the first paragraph now reads,

    ``As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously-published compatibility inequalities of Wolfe et al. [21], as well as against the entropic inequalities of Henson et al. [19]. For historical context, the entropic inequalities of [19] have already been independently investigated for quantum incompatibility by Weilenmann and Colbeck [20] using a variety of computational methods. Unfortunately, these methods failed to identify quantum-accessible distributions capable of violating any of the entropic inequalities considered by [20]. Additionally, the inequalities presented in [21] have not been previously investigated numerically.''

    For even more context (excluded from Section VI for brevity), entropic inequality constraints for the Triangle structure first appeared in Fritz, Chaves [40], but a completed list of all Shannon-type entropic inequalities could not be computed due to the computational limitations of Fourier Motzkin. In Chaves, Luft, and Gross [17], these computational limitations were overcame using all conditional independence constraints to pre-process the Fourier Motzkin procedure and produced two new entropic inequalities. To the best of our knowledge, attempts to violate these inequalities using computational methods first appeared in [20].
    }

    \ccomment{In addition, I am a bit puzzled by the following comment "These early results suggest that there is no quantum-classical gap in the Triangle structure for two-outcome measurements". Although I am personally prepared to believe this for various reasons, I do not see how the numerical study of the particular inequalities of [21] and [19] justifies it?}

    \response{
    You are correct. Strictly speaking, the numerical failings are inconclusive. The purpose of the `conjecture' was to narratively motivate the shift to larger-outcome inequalities. The document reflects this change of perspective:

    ``Unfortunately, these early results are inconclusive for two reasons. First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states. Second, there is little reason to suggest that the inequalities considered in [21] are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.

    Nonetheless, having seen no quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.''
    }

    \ccomment{ Disregarding that (what I understand is) optimization from the interior of the quantum set, cannot prove the correctness (indeed only “suggest” the correctness) of such a statement, one would still need to know a thing or two about the properties of the inequalities considered. For example, the classical set is non-convex so there is no notion of a facet. Are the inequalities in [21] and [19] `optimal', so that the inability to violate them somehow indicates the lack of a quantum advantage for any inequality? If yes, what would it mean that an inequality in a non-convex setting is optimal? Furthermore, is it uniquely optimal, or can there be other unknown optimal inequalities where we could find a quantum violation? In summary, I wonder whether the claim is properly motivated.}

    \response{
        Excellent question. Evidently, the notion of a facet breaks down when the set of classical correlations no longer forms a polytope. The Triangle structure is an instance of this breakdown. Nonetheless, new results due to Rosset, Wolfe (https://arxiv.org/abs/1709.00707) reveal that it is possible to generalize the notion of an 'optimal' inequality.

        Explicitly, in 1709.00707, it was proven that the set of compatible classical distributions for any causal network (including the Triangle structure) forms a semi-algebraic set; meaning that there exists a \textit{finite} list of inequality and equality constraints that are necessary and sufficient for accessing compatibility. Therefore, an inequality belonging to this necessary and sufficient set may be considered as optimal. Geometrically, an inequality is considered `tight' if its intersection with the classical/compatible set is full-dimensional.

        Determining whether or not any given inequality is optimal in this sense is still poorly understood and certainly worthy or further research. For the sake of brevity, we elected to include the following sentence to Section VI.

        ``Second, there is little reason to suggest that the inequalities considered in [21] are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.''
    }

    \ccomment{Regarding the new inequalities. Do the authors have some intuition for what type of inflations leads to interesting inequalities? It is stated that larger inflations were needed, as compared to those of ref [21]. Is it the case that the larger the inflation, the stronger the inequality? Furthermore, as far as I understand, a given inflations leads to many possible inequalities. Is there natural way to identify the interesting inequalities, or must check them one by one to find the interesting results? Again, if the authors have developed further intuition for such practically relevant matters of how to best use inflation, it would be good to mention it in the main text.}

    \response{
        Excellent questions. Your intuition is correct, larger inflations lead to stronger inequalities. This is proven in [22] by demonstrating that the Inflation Technique is capable of completely solving the causal compatibility problem. Explicitly, if a distribution is incompatible with a causal structure, then there exists a sufficiently large inflation capable of generating an inequality which witnesses its incompatibility. Nonetheless, the inequalities derived in the paper came from relatively small inflations. Our revision of the paper now expands on this point,

        ``The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations [22]. Consequently, the derivation of Ineqs. (13,15,12) is guaranteed by [22] for sufficiently large inflations. Nonetheless, the following inequalities were obtained using the relatively small inflations found in Fig. 8.''

        In a footnote,
        ``Note that the adjectives large and small used to describe an inflation only become well-defined in the context of the hierarchy proposed in [22]. For example, the Web Inflation in Fig. 8c is second in the hierarchy of [22] whereas the Wagon-Wheel Inflation in Fig. 8b is somewhere between the first and second order.''

        Regarding the generation of many possible inequalities, you are correct. In the absence of a particular distribution, the Inflation Technique yields a plethora of inequalities, many of which are redundant (strictly speaking, this problematic feature is shared among many inequality-deriving techniques which use linear (or non-linear) quantifier elimination). If the objective is to identify which of the non-redundant inequalities admit quantum violations, the best method (for the moment) is to check them one by one. However, in this paper we used a method (explained in Appendix C) for deriving inequalities in the presence of a particular distribution, namely the Fritz distribution. This method only produces inequalities which by construction are violated by the Fritz distribution already; therefore we avoid having to distinguish the interesting inequalities from the uninteresting ones. As such, the task of eliminating uninteresting inequalities never naturally arises in this paper. Moreover, the original Inflation paper [21] addresses most of these concerns and comments in a more universal setting (i.e. for any causal structure, not just the Triangle structure), and consequently, we have found it best to omit the topic from this paper.
    }

    \ccomment{Regarding genuine quantum triangle correlations. I fully agree with the authors that the Fritz distribution is manufactured to fit the triangle scenario based on the well-known CHSH violations. Indeed, this is not a genuine triangle correlation. This is sufficient to convince a reader that not all quantum violations of a triangle inequality are qualitatively interesting. However, an important issue would be to define what it means that a quantum triangle correlation is not based on Bell's theorem. The authors inherit this question from the work of Fritz. Although agreeing with the intuition, I think the intuition for this question is not yet sufficiently developed to be phrased as a meaningful question. Basically, what does it mean for a general probability distribution in the triangle not to be based on Bell's theorem?}

    \response{
        See our response to \textbf{1.14}.
    }

    \ccomment{The authors have derived a triangle inequality with a quantum violation that is not identical to the Fritz distribution. Nevertheless, they make the following comment (in the conclusions):}

    \ccomment{"Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure. Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality."}

    \ccomment{The inability to address my above question (what does it mean for triangle correlations not to be based on Bell's theorem?) hinders the authors to make a clear conclusion about their not-identical-but-quite-similar-to-Fritz's distribution. I would consider this an important question since it is essential to how strong a conclusion can be drawn from one of the key result of the paper. I am mildly surprised that the authors did not make an effort to at least partially address this matter. Perhaps the question could (at least) be rigorously formulated, i.e., a reasonable definition could be provided for what it means for triangle correlations not to be based on Bell's theorem. However, without knowing how such a definition may look, I suspect that resolving the question will not be straightforward. Nevertheless, it may be worth it for the authors to draw some attention to this poorly defined but clearly relevant idea.}

    \response{
        This comment \textbf{1.14} and the above comment \textbf{1.11} will be answered here.

        Determining whether or not a given quantum correlation incompatible with the Triangle structure expresses genuine, novel forms of non-classicality is, at the moment, not yet a sufficiently developed decision problem as you mention. Moreover, we completely agree that is worth drawing attention to this clearly relevant idea. As such, we have included in the paper submission a new section that precedes the conclusion titled Revisiting Fritz's Problem. In this section, we consider a few avenues for formalizing this idea, and point out a deficiency for each. Ultimately, this additional section fails to rigorously reformulate Fritz's problem, but at least provides the reader with an understanding for the importance of doing so.
    }

    \clearpage
    \stepcounter{refereecounter}
    \section{Responses to Second Referee}

    \ccomment{This paper reports on the use of the inflation technique to derive inequalities for the triangle causal structure that admit quantum violations. The triangle causal structure is a well-studied example and seems to be resistant to being solved elegantly. The authors make progress on this difficult problem, while still not getting to an elegant solution. However, the progress they make is interesting and qualitatively different to before, since the inequalities found are the first that are known to have quantum violations (there are many existing inequalities not known to have such violations).}

    \ccomment{I am happy to recommend this be accepted subject to minor changes.}{}

    \ccomment{
    More detailed remarks/comments/questions:

    Introduction:

    It is perhaps a bit strong to claim that *every* aspect of quantum phenomena that is non classical had led to practical exploitation for computation or communication. [note the typo "of"-\textgreater"or" shortly before [4]]
    }

    \response{Agreed. Typo corrected. Modified sentence: ``Throughout history, numerous quantum phenomena which fail to be emulated by classical physics have been identified as resources for solving computational or communicational problems.''}

    \ccomment{Sentence "This work is the first therefore...", should perhaps say "known" rather than "able"}

    \response{Corrected.}

    \ccomment{Related to the same paragraph, isn't is implied by [22] that such inequalities must exist in principle? Is one conclusion of the present paper that one doesn't have to go too far down the inflation chain to find one?}

    \response{
        Correct, [22] proves that some inequality will be found at some sufficiently high order in the inflation hierarchy. The inflations consider in this paper are all relatively low on the hierarchy. However, when one expects to find an inequality (if there is one) is still poorly understood. For example, in [28] there is a $4$-outcome distribution for the Triangle structure which is conjectured to be incompatible and yet it passes the second order inflation tests failed by the Fritz distribution. The following addition is made to Section V II:

        ``The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations [22]. Consequently, the derivation of Ineqs. (13,15,12) is guaranteed by [22] for sufficiently large inflations. Nonetheless, the following inequalities were obtained using the relatively small inflations found in Fig. 8. This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the 4-outcome distribution proposed by [28] is not confirmed by Inflation Technique at the same level.''

        See also response \textbf{1.10}.
    }

    \ccomment{
    Sec II:

    Sentence "Specifically, the causal structure G hypothesizes..." has grammatical issues.}

    \response{Agreed. Modified sentence: ``A causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is only directly influenced by its parents $\Pa[\graph]{n}$.''.}

    \ccomment{Near the end of Sec II, "complete characterization for any causal structure": this remark clashed with a later remark on p5 that Bell's structure has a "complete classification of classicality".}

    \response{Corrected: Currently however, it is unknown how to obtain a complete characterization for all causal structures, including the Triangle structure.}

    \ccomment{
    Sec III:

    typo "asses"-\textgreater"assess"}

    \response{Corrected.}

    \ccomment{In (2) there is a P\_lambda missing after the sum.}

    \response{This is a typo in the ArXiv submission and was corrected for our PRA submission.}

    \ccomment{
    Sec V:

    Perhaps change "We close this loophole..." to "This loophole is closed..." to make clear this is not a new idea here.}

    \response{Corrected: ``This loophole is closed by having...''.}

    \ccomment{
    Sec VII A:

    Last paragraph, maybe write P\_ABC as P\_\{A\_lA\_rB\_lB\_rC\_lC\_r\} or mention equivalence: if I understand correctly, the alphabet size must be 4 for each of A, B and C to use (11).}

    \response{
        Apologies for the confusion, this equivalence has now been explicitly mentioned. Moreover, we believe that the ordering of statements in Section V made it very confusing for any reader to understand the two different, but isomorphic notations. As such, we have made slight modifications to Section V to make this correspondence clear for future readers.
    }

    \ccomment{typo "distribution very similar to P\_F itself" -\textgreater "distributions"}

    \response{Corrected.}

    \ccomment{Do you have any insights as to why the particular inflations considered turn out to be useful? Do you have any insight as to which inflations are likely to be useful?}

### 2018-06-07 CCIAQVTS/CCIAQVTS.tex
First completed draft of the referee responses

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).

@@

    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments. First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure. Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality \cite{Navascues_2017}. Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality. The authors attempts to find such novel resources were met with only partial success, suggesting clear refinements for future exploration.

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution first was proven to be non-classical without the use of inequalities. Here we offer a direct proof using inequalities, with the advantage that our proof is robust to noise. A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Additionally, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new flavors of non-classicality in the Triangle structure. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution is deemed \textit{incompatible}.  Conversely, a singular inequality can only be used to prove that a given distribution is \textit{incompatible}; a single inequality cannot certify compatibility. A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifies compatibility. Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the Triangle structure.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    The exemplifying quantum distribution corresponding to a recasting of a non-classical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}. In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$. It is convenient to represent the outcomes using two binary digits, $\bc{00,01,10,11}$. Explicitly, $\prob[\fritz]$ can be written as:

@@

    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
    The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block. When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by (i.e. perfectly correlated with) the outcome of $C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded}, the left-hand bits $A_l$ and $B_l$ emulate the measurement settings $S_{A}$ and $S_{B}$, whereas the right-hand bits $A_r$ and $B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure (\cref{fig:bell_structure}). Critically, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.

>>>>

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).

@@

    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments. First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure. Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum non-classicality \cite{Navascues_2017}. Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality. The authors attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.

    The first half of the manuscript, namely \Cref{sec:causal_compatibility,sec:bell_structure,sec:triangle_structure,sec:fritz_distribution}, is entirely a review of previous works. \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be non-classical without the use of inequalities.

    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project. Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}. A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}. Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities. First, an inequality-based proof has the advantage of being robust to experimental noise. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory. The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel non-classicality in the Triangle structure. \Cref{sec:conclusions} concludes.

@@

    If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution is deemed \textit{incompatible}.  Conversely, a singular inequality can only be used to prove that a given distribution is \textit{incompatible}; a single inequality cannot certify compatibility. A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifies compatibility. Currently however, it is unknown how to obtain a complete characterization for all causal structures, including the Triangle structure.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    The exemplifying quantum distribution corresponding to a recasting of a non-classical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}. In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$. Explicitly, $\prob[\fritz]$ can be written as:

@@

    In~\cref{eq:fritz_dist}, the notation $\prob[\fritz][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}. When expressing the outcomes $\bc{0,1,2,3}$ as pairs of binary digits $\bc{00, 01, 10, 11}$, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by the outcome of $C$.
    \eq \label{eq:fritz_dist_bit_variant}
        \prob[\fritz][00,00,00] = \prob[\fritz][01,01,00] = \prob[\fritz][00,10,01] = \prob[\fritz][01,11,01] &= \f{1}{32}\br{2 + \sqrt{2}} \\
        \prob[\fritz][10,00,10] = \prob[\fritz][11,01,10] = \prob[\fritz][10,11,11] = \prob[\fritz][11,10,11] &= \f{1}{32}\br{2 + \sqrt{2}} \\
        \prob[\fritz][00,01,00] = \prob[\fritz][01,00,00] = \prob[\fritz][00,11,01] = \prob[\fritz][01,10,01] &= \f{1}{32}\br{2 - \sqrt{2}} \\
        \prob[\fritz][10,01,10] = \prob[\fritz][11,00,10] = \prob[\fritz][10,10,11] = \prob[\fritz][11,11,11] &= \f{1}{32}\br{2 - \sqrt{2}}
    % = \prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}]
